Ceph Parallel File System Evaluation Report

### 2013-08-29 ceph-initial.tex
fix graphing color, remove commands, fit in 8 pages

After running diagnostics, we observed that outstanding operations on the
clients were not being shown as outstanding on the OSDs.  This appeared to be
very similar to a problem Jim Schutt at Sandia National labs encountered with
TCP autotuning in the Linux
kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this improving the performance
significantly on Ceph read operations. As shown in
Figure~\ref{fig:rados-tcp-autotune-disabled}.

@@

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on number of OSDs: single server single client}
\label{fig:osd-scale}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on number of servers, with 8 clients}
\label{fig:oss-scale}
\end{figure}

In this test, we exercise OSD servers from one to four, driven by four hosts
each with four RADOS Bench process. Each additional OSD server adds eleven
more OSDs into play. The results are illustrated in
Figure~\ref{fig:oss-scale}. We notice that the read performance improved about
10% given eight clients instead of four, but write performance is mostly flat
for reason explained below. We also observe that Ceph exhibits linear scaling
with regard to number of servers, at least in the given number of servers.
However, the peak performance we are seeing is about the half of what are
expecting from the SFA10K (compare to the baseline block I/O performance
number presented in Section~\ref{sec:block-io}).

@@

@@

We used the synthetic IOR benchmark
suite\footnote{\url{http://sourceforge.net/projects/ior-sio/}} for file system
level performance and scalability test.  The particular parameter setup is show
in Table \ref{tbl:ior}. Each client node has 6 GB of physical memory, the block
size is set so as to mitigate cache effects. In addition, the test harness
program issues the following commands at the beginning of each test:

@@

Our first round of tests was less than ideal as we encountered various issues. For
the sake of completeness, we first summarize the results, then discuss
further tuning efforts and improvements.

The full permutation of IOR parameters were not explored due to I/O errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
(4) and fixed block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

  \item The write performance is also about half of what we can obtain from
  RADOS Bench. When number of clients reaches 8, there is a significant
  performance drop as well.

>>>>

After running diagnostics, we observed that outstanding operations on the
clients were not being shown as outstanding on the OSDs.  This appeared to be
very similar to a problem Jim Schutt at Sandia National labs encountered with
TCP autotuning in the Linux
kernel\cite{Jim:tcptune}.
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product.

@@

With this change in place, We have observed this improving the performance
significantly on Ceph read operations. As shown in
Figure~\ref{fig:rados-tcp-autotune-disabled}.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on number of OSDs: single server single client}
\label{fig:osd-scale}
\end{figure}

@@

In this test, we exercise OSD servers from one to four, driven by four hosts
each with four RADOS Bench process. Each additional OSD server adds eleven
more OSDs into play.  Figure~\ref{fig:oss-scale} summarized the results.
Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
performance improved about 10\% given eight clients instead of four, but write
performance is mostly flat for reason explained below. We also observe that
Ceph exhibits linear scaling with regard to number of servers, at least in the
given number of servers.  However, the peak performance we are seeing is about
the half of what are expecting from the SFA10K (compare to the baseline block
I/O performance number presented in Section~\ref{sec:block-io}).

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on number of servers, with 8 clients}
\label{fig:oss-scale}
\end{figure}

@@

We used the synthetic IOR benchmark
suite\cite{ior} for file system
level performance and scalability test.  
Each client node has 6 GB of physical memory, the block
size is set so as to mitigate cache effects. In addition, the test harness
program issues commands at the beginning of each test to free pagecache,
dentries and inodes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%   COMMENT OUT IOR parameter table 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}

@@

\end{comment}

Our initial tests was less than ideal as we encountered various issues.  The
full permutation of IOR parameters sweep were not explored due to I/O errors
we encountered.  We were, however, able to record results in two extreme cases
as far as transfer size is concerned: 4 KB and 4 MB, using a fixed number of
OSD servers (4) and fixed block size (8 GB), the results are illustrated in
Figure \ref{fig:ior4k} and \ref{fig:ior4m}, we make the following
observations:

@@

  \item The write performance is also about half of what we can obtain from
  RADOS Bench. When number of clients reaches 8, there is a significant
  performance drop, which is a poor sign for scalability.

### 2013-08-29 ceph-tuning.tex
fix graphing color, remove commands, fit in 8 pages

@@

Even with these two changes in place, less-than-ideal write performance and
very poor read performances were observed during our tests.  We also observed
that by increasing the number of IOR processes per client node, the read
performance degraded even further indicating some kind of contention either on
the clients or on the OSD servers.

@@

At this point, we were able to both make more client nodes available for Ceph
file system-level testing and also install a profiling tool called \verb!perf!
that is extremely useful for profiling both kernel and user space codes.
Profiling with \verb!perf! showed high CPU utilization on test clients due to
CRC32c processing in the Ceph kernel client.  CRC32 checksums can be disabled
by changing the CephFS mount options:

\begin{Verbatim}[fontsize=\small]
mount -t ceph 10.37.248.43:6789:/ 
    /mnt/ceph -o name=admin,nocrc
\end{Verbatim}

@@

We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
test.  The results were extremely positive and presented in
Figure~\ref{fig:rados-kernel}.

@@

As can be seen, with the 3.9 kernel, while there was a slight improvement on
write performance, read performance improved dramatically.  In addition to the
kernel change, the amount of CephFS
client kernel read-ahead cache size was improved as:

\begin{Verbatim}[samepage=true, fontsize=\small]
mount -t ceph 10.37.248.43:6789:/ 
  /mnt/ceph -o name=admin,nocrc,
  readdir_max_bytes=4104304,
  readdir_max_entries=8192
\end{Verbatim}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% removed for space

@@

Even with these changes in place, less-than-ideal write performance and very
poor read performances were observed during our tests.  We also observed that
by increasing the number of IOR processes per client node, the read
performance degraded even further indicating some kind of contention either on
the clients or on the OSD servers.

@@

At this point, we were able to both make more client nodes available for Ceph
file system-level testing and also install a profiling tool called \verb!perf!
that is extremely useful for profiling both kernel and user space codes.
Profiling with \verb!perf! showed high CPU utilization on test clients due to
CRC32c processing in the Ceph kernel client.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% removed

%CRC32 checksums can be disabled
%by changing the CephFS mount options:

%\begin{Verbatim}[fontsize=\small]
%mount -t ceph 10.37.248.43:6789:/ 
%    /mnt/ceph -o name=admin,nocrc
%\end{Verbatim}

@@

We upgraded our test systems with kernel version 3.9 and performed RADOS Bench
test.  The results were extremely positive and presented in
Figure~\ref{fig:rados-kernel}. As can be seen, with the 3.9 kernel, while
there was a slight improvement on write performance, read performance improved
dramatically.  In addition to the kernel change, the amount of CephFS client
kernel read-ahead cache size was increased as well.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% REMOVED to save space

%\begin{Verbatim}[samepage=true, fontsize=\small]
%mount -t ceph 10.37.248.43:6789:/ 
%  /mnt/ceph -o name=admin,nocrc,
%  readdir_max_bytes=4104304,
%  readdir_max_entries=8192
% \end{Verbatim}
